Mixed effect tweedie model in TMB

### 2020-06-19 analysis/tmb-sensor-explore/3-fit-do.Rmd
refining climate models

# get scaling used in model
sensor_temp_scaled <- scale(d_trawl$temp)
attributes(sensor_temp_scaled)

predtemp <- pred_temp %>% mutate(
  temp_scaled = (est - attributes(sensor_temp_scaled)[[2]] )/attributes(sensor_temp_scaled)[[3]], 
  temp_scaled2 = (temp_scaled)^2) %>% select(-est, -est_non_rf, -est_rf, -omega_s, -zeta_s, -epsilon_st)
predtemp <- predtemp %>% filter(year > 2007) 
predtemp$DOY_scaled <- 0

@@

# rename and back transform climate variables
pred_do$temp <- pred_do$temp_scaled * attributes(sensor_temp_scaled)[[3]] + attributes(sensor_temp_scaled)[[2]]
pred_do$log_do <- pred_do$est
pred_do$do_est <- exp(pred_do$log_do)

# may want to filter estimates for depths less than 15 m
# pred_do <- pred_do %>% filter(depth>15)

saveRDS(pred_do, file=here::here("analysis/VOCC/data/predicted-DO-depth2.rds"))
```

>>>>

predtemp <- pred_temp %>% mutate(
  temp = est,
  temp_omega = omega_s,
  temp_epsilon = epsilon_st,
  temp_scaled = (est - model2$data$temp_mean[1])/model2$data$temp_sd[1], 
  temp_scaled2 = (temp_scaled)^2) %>% select(-est, -est_non_rf, -est_rf, -omega_s, -zeta_s, -epsilon_st)
predtemp <- predtemp %>% filter(year > 2007) 
predtemp$DOY_scaled <- 0

@@

# rename and back transform climate variables
pred_do$log_do <- pred_do$est
pred_do$do_est <- exp(pred_do$log_do)

# may want to filter estimates for depths less than 15 m
# pred_do <- pred_do %>% filter(depth>15)
saveRDS(pred_do, file=here::here(paste0("analysis/VOCC/data/predicted-DO-", Sys.Date(),".rds")))
```
